### 2019-04-25 paper_04_shallow_water/Latex/article.tex
Fix duplicate refs

The $ k^{-5/3} $ spectrum has been reproduced 
 by some General Circulation Models (GCM:s) based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008}.  \cite{AugierLindborg2013}  formulated a spectral energy budget of kinetic and available potential energy in terms of spherical harmonics and used this formulation to investigated two GCM:s. It was found that one of the models -- named the AFES model -- was able to reproduce a downscale energy cascade with realistic $ k^{-5/3} $ mesoscale spectra. The result was almost too good, since the AFES model simulation only contained 21 vertical levels, while theoretical arguments based on stratified turbulence theory \cite[]{Lindborg2006} suggest that a much finer vertical resolution would be needed. This lead us to ask what number of vertical levels a model needs in order  to reproduce a downscale energy cascade. Was \cite{YuanHamilton1994}  right  when they suggested that even a single layer model, such as the SW equations, could do the job? 
The original motivation of this study was to investigate this suggestion. A first set of simulations of the SW equations, containing both balanced and gravity wave motions, showed some encouraging results. Indeed, gravity waves were transferring energy towards small scales. However, after a while it became clear that the cascade was not as strong as in the GCM simulation.  Moreover, in all the SW simulations we observed shocks with an associated $ k^{-2} $-spectrum rather than a $ k^{-5/3} $-spectrum. These observations lead us to dismiss the SW equations as a model for the atmospheric downscale cascade. Based on the SW equations we developed another two-dimensional toy model  \cite[]{LindborgMohanan} that is absent of shocks and can reproduce the energy cascade in the GCM quite well, including a $ k^{-5/3}  $-spectrum.

@@

%
Time advancement is carried out by a classical fourth-order Runge-Kutta scheme
for the nonlinear term and an exact integration for the linear and dissipative
terms. This explicit integration is especially useful at very high resolution
and very large $c$ when the shortest waves are very fast. We use an adaptable
time step method which maximizes the time step over a standard
Courant-Friedrichs-Lewy condition \cite[]{Lundbladh1999, AugierChomazBillant2012}.
%
Most of the aliasing is removed by truncating 8/9 of the modes along each
direction \cite[for a detail discussion on the issues of the non-conservation
of the non-quadratic energy and the aliasing errors in the truncated one-layer
shallow water model, see][]{FargeSadourny1989}. The resolution is characterised
by the number of nodes, $n$, in each direction and has been varied from 960
to 7680.
%
The wave speed $c$ has been varied over almost two orders of magnitude from 10
to 700. The wave modes are forced in a shell in spectral space corresponding to
relatively small wave numbers, $ 5 \delta k < |\kk| < 8 \delta k$, where $
\delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
domain.  We define the forcing wave number as $ k_f = 6 \delta k $. To obtain as broad scaling range as possible it is preferable to choose 
the forcing scale, $ L_f = \pi/k_f $, as large as possible. On the other hand, if $ L_f $ is too large, there is a risk that standing waves will be induced by the periodic boundary conditions and also that isotropy will be broken due to alignment of the shocks with the boundaries. 
We have found that $ L_f/L =1/12 $ is sufficient to avoid these two problems. 
The forcing is white noise in time and designed so that the energy
injection rate is normalised to unity at each time step. When the flow has reached a stationary state dissipation should therefore be equal to unity. 
The strength of the stratification is characterised by a
Froude number, defined as
\begin{equation} \label{Fr}
F_f = \frac{(\epsilon L_f)^{1/3}}{c} \, ,
\end{equation}
a parameter that can be determined from the start of each simulations.
Energy is dissipated at the smallest resolved scales by hyperviscosity. An intricate question is how the value of $ \nu_{8} $ should be chosen so that the shocks are resolved. The standard resolution requirement in turbulence simulations of this type is that the hyperviscosity analogue to the Kolmogorov scale
\begin{equation}  \label{KolmEight}
\eta_{8} = \left( \frac{{\nu_8}^3}{\epsilon} \right)^{\frac{1}{22}},
\end{equation}
should be resolved. However, our estimate (\ref{Width}) of the shock width suggests that this may not be a sufficient condition, since $ d $ is likely to enter the expression for $ \delta x $ also in the case when we use hyperviscosity.
A similar estimate as in (\ref{Estimate}) gives
\begin{equation} \label{EtaEight}
\delta x \sim \eta_{8} \left ( \frac{\eta_8}{d} \right)^{1/21} \, .
\end{equation} 
Thus, the shock width dependence on $ d $ can be expected to be extremely weak when hyperviscosity is used. Therefore we simply use the standard resolution requirement that (\ref{KolmEight}) should be resolved. We have found that setting
$  k_{d} \simeq \kmax/ 2.5$, where $ k_{d} = 1/\eta_8 $ and $\kmax =
(8/9)\pi n/L $ is the maximum wave number, is  sufficient to resolve the shocks. Since the energy injection rate is normalised to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state. 
 The  simulation parameters are listed in table 1.

>>>>

The $ k^{-5/3} $ spectrum has been reproduced 
 by some General Circulation Models (GCM:s) based on the primitive
equations \cite[]{KoshykHamilton2001, Skamarock2004,
Hamilton_etal2008}.  \cite{AugierLindborg2013}  formulated a spectral energy budget of kinetic and available potential energy in terms of spherical harmonics and used this formulation to investigated two GCM:s. It was found that one of the models -- named the AFES model -- was able to reproduce a downscale energy cascade with realistic $ k^{-5/3} $ mesoscale spectra. The result was almost too good, since the AFES model simulation only contained 21 vertical levels, while theoretical arguments based on stratified turbulence theory \cite[]{Lindborg2006} suggest that a much finer vertical resolution would be needed. This lead us to ask what number of vertical levels a model needs in order  to reproduce a downscale energy cascade. Was \cite{YuanHamilton1994}  right  when they suggested that even a single layer model, such as the SW equations, could do the job? 
The original motivation of this study was to investigate this suggestion. A first set of
simulations of the SW equations, containing both balanced and gravity wave motions,
showed some encouraging results. Indeed, gravity waves were transferring energy towards
small scales. However, after a while it became clear that the cascade was not as strong
as in the GCM simulation.  Moreover, in all the SW simulations we observed shocks with
an associated $ k^{-2} $-spectrum rather than a $ k^{-5/3} $-spectrum. These
observations lead us to dismiss the SW equations as a model for the atmospheric
downscale cascade. Based on the SW equations we developed another two-dimensional toy
model  \cite[]{LindborgMohanan2017} that is absent of shocks and can reproduce the
energy cascade in the GCM quite well, including a $ k^{-5/3}  $-spectrum.

@@

%
Time advancement is carried out by a classical fourth-order Runge-Kutta scheme
for the nonlinear term and an exact integration for the linear and dissipative
terms. This explicit integration is especially useful at very high resolution
and very large $c$ when the shortest waves are very fast. We use an adaptable
time step method which maximizes the time step over a standard
Courant-Friedrichs-Lewy condition \cite{Lundbladh1999, AugierChomazBillant2012}.
%
Most of the aliasing is removed by truncating 8/9 of the modes along each
direction \cite[for a detail discussion on the issues of the non-conservation
of the non-quadratic energy and the aliasing errors in the truncated one-layer
shallow water model, see][]{FargeSadourny1989}. The resolution is characterised
by the number of nodes, $n$, in each direction and has been varied from 960
to 7680.
%
The wave speed $c$ has been varied over almost two orders of magnitude from 10
to 700. The wave modes are forced in a shell in spectral space corresponding to
relatively small wave numbers, $ 5 \delta k < |\kk| < 8 \delta k$, where $
\delta k = 2 \pi /L $ and $ L $ is the length of the side of the quadratic
domain.  We define the forcing wave number as $ k_f = 6 \delta k $. To obtain as broad scaling range as possible it is preferable to choose 
the forcing scale, $ L_f = \pi/k_f $, as large as possible. On the other hand, if $ L_f $ is too large, there is a risk that standing waves will be induced by the periodic boundary conditions and also that isotropy will be broken due to alignment of the shocks with the boundaries. 
We have found that $ L_f/L =1/12 $ is sufficient to avoid these two problems. 
The forcing is white noise in time and designed so that the energy
injection rate is normalised to unity at each time step. When the flow has reached a stationary state dissipation should therefore be equal to unity. 
The strength of the stratification is characterised by a
Froude number, defined as
\begin{equation} \label{Fr}
F_f = \frac{(\epsilon L_f)^{1/3}}{c} \, ,
\end{equation}
a parameter that can be determined from the start of each simulations.
Energy is dissipated at the smallest resolved scales by hyperviscosity. An intricate question is how the value of $ \nu_{8} $ should be chosen so that the shocks are resolved. The standard resolution requirement in turbulence simulations of this type is that the hyperviscosity analogue to the Kolmogorov scale
\begin{equation}  \label{KolmEight}
\eta_{8} = \left( \frac{{\nu_8}^3}{\epsilon} \right)^{\frac{1}{22}},
\end{equation}
should be resolved. However, our estimate (\ref{Width}) of the shock width suggests that this may not be a sufficient condition, since $ d $ is likely to enter the expression for $ \delta x $ also in the case when we use hyperviscosity.
A similar estimate as in (\ref{Estimate}) gives
\begin{equation} \label{EtaEight}
\delta x \sim \eta_{8} \left ( \frac{\eta_8}{d} \right)^{1/21} \, .
\end{equation} 
Thus, the shock width dependence on $ d $ can be expected to be extremely weak when hyperviscosity is used. Therefore we simply use the standard resolution requirement that (\ref{KolmEight}) should be resolved. We have found that setting
$  k_{d} \simeq \kmax/ 2.5$, where $ k_{d} = 1/\eta_8 $ and $\kmax =
(8/9)\pi n/L $ is the maximum wave number, is  sufficient to resolve the shocks. Since the energy injection rate is normalised to unity and all simulations reach a stationary state in which dissipation is equal to the injection rate, $ \nu_8 $ can be chosen already from the start so that this condition will be fulfilled in the stationary state. 
 The  simulation parameters are listed in table 1.
